\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-07-25 feedback.tex
add PEIO, CEA and Midwest 2014 feedback to to-do

\newpage
\subsection {Summer 2015 CEA}
\begin{itemize}
	\item Richard: what happens if $\ga(e^L) < \ga(s^H)$?
	\item Dev: Reputation: do they use safeguards less b/c worried about reputation?
	\item Chris: What is an exogenous shock to political pressure? What signal would be correlated?
\end{itemize}

\vskip.5in
\subsection{January 2016, PEIO Salt Lake City}
\begin{itemize}
	\item Elias Bengtsson: more on policy implications, who's doing what to whom
	\item Cristiane Carneiro
		\begin{itemize}
			\item Flexible instruments
			\item Agreement duration, exit (legal scholarship)
			\item Look at Summer 2001 special edition of IO
			\item Korgmenos 2013 JCR
			\item Korgmenos and Nav 2011
			\item Coil
			\item Helper 2005, Virginia Law Review
		\end{itemize}
	\item Renee Bowen: what's the contribution relative to GH; her paper, Peter's, McLaren (but she was a bit confused about what I was doing we figured out later)
	\item Competing lobbies--exporters
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover
\end{itemize}

\newpage
\section{Feedback on 2014 draft}
\subsection{May 30, 2014, Spring Midwest meetings}
\begin{itemize}
	\item Rick Bond, Ian Wooton, James Lake, Mostafa, David Kuenzel at the talk
	\item Rick: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
	\item James: need to be more precise about when $\ga$ is evaluated
		\begin{itemize}
			\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
		\end{itemize}
	\item Ex-ante lobbying: need to understand MRC07 result that tariff-cap = strong binding
\end{itemize}

>>>>

\newpage
\subsection {Summer 2015 CEA}
\begin{itemize}
	\item Richard: what happens if $\ga(e^L) < \ga(s^H)$? [done]
	\item Dev: Reputation: do they use safeguards less b/c worried about reputation? [outside the scope]
	\item Chris: What is an exogenous shock to political pressure? What signal would be  correlated? [don't think I need to go there]
\end{itemize}

\vskip.5in
\subsection{January 2016, PEIO Salt Lake City}
\begin{itemize}
	\item Elias Bengtsson: more on policy implications, who's doing what to whom [done]
	\item Cristiane Carneiro
		\begin{itemize}
			\item Flexible instruments
			\item Agreement duration, exit (legal scholarship)
			\item Look at Summer 2001 special edition of IO
			\item Korgmenos 2013 JCR
			\item Korgmenos and Nav 2011
			\item Coil
			\item Helper 2005, Virginia Law Review
		\end{itemize}
	\item Renee Bowen: what's the contribution relative to GH; her paper, Peter's, McLaren (but she was a bit confused about what I was doing we figured out later) [done / don't need to do]
	\item Competing lobbies--exporters [outside scope]
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover [on to-do list]
\end{itemize}

\newpage
\section{Feedback on 2014 draft}
\subsection{May 30, 2014, Spring Midwest meetings}
\begin{itemize}
	\item Rick Bond, Ian Wooton, James Lake, Mostafa, David Kuenzel at the talk
	\item Rick: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$ [on to-do list]
	\item James: need to be more precise about when $\ga$ is evaluated [on to-do list]
		\begin{itemize}
			\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
		\end{itemize}
	\item Ex-ante lobbying: need to understand MRC07 result that tariff-cap = strong binding [been there, done that, got the t-shirt, gave it back]
\end{itemize}

### 2016-07-25 to-do.tex
integrate Ryerson feedback into to-do
add ETSG 2014 and McGill feedback to to-do
add PEIO, CEA and Midwest 2014 feedback to to-do

\section{Misc.}
\begin{itemize}
	\item Define $\ga$ before using it
	\item If add back in assumption 1, add Ethier footnote
	\item standardize $\ga(e,s)$, $\ga(e)$, $\ga(s)$ throughout the text
\end{itemize}

\section{Deal with ``dynamic preferences'' issue}
		\begin{itemize}
			\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item DILLENBERGER, D., J. S. LLERAS, P. SADOWSKI, AND N. TAKEOKA (2013): ``A Theory of Subjective Learning,'' Working Paper. 
					\item GUL, F., AND W. PESENDORFER (2004): ``Self-Control and the Theory of Consumption,'' Econometrica, 72 (1), 119-158
					\item JONES, R. A., AND J. M. OSTROY (1984): ``Flexibility and Uncertainty,'' Review of Economic Studies, 51 (1), 13-32
					\item KOOPMANS, T. C. (1964): ``On the Flexibility of Future Preferences,'' in Human Judgments and Optimality, ed. by M. W. Shelly and G. L. Bryan. New York: Wiley.
					\item KREPS, D. M., AND E. L. PORTEUS (1978): ``Temporal Resolution of Uncertainty and Dynamic Choice Theory,'' Econometrica, 46 (1), 185-200.
				\end{itemize}
		\end{itemize}
\section{Take out repeats}
	Especially of references to BS2005: In some parts the paper also seem repeating itself: you review Bagwell and Staiger (2005) in Section 2.2 but you provide another summary of the same paper in Section 3. Again, a revised structure may reduce the overlap, make the paper shorter, and be more to the point.

@@

\section{Lit review}
\begin{itemize}
	\item Find MRC cites (maybe some in Ethier) for why PE shocks can't be addressed
		\begin{itemize}
			\item Bagwell and Staiger 1999 AER
		\end{itemize}
	\item Have to make connection to endogenous papers clearer
	\item Review Bown, Bagwell $\&$ Staiger
	\item Do I include papers like BS2001 (non-repeated) in lit review?
	\item Limao and Tovar 2011
		\begin{enumerate}
			\item Their 2nd (and final) stage is Nash bargaining. Is there an isomorphism to my setup?
			\item It IS clear to take their first, limited case of commitment to tariff cap only (ignore NTB) as analogy for gov't in my model choosing commitment to different tariff level. Need to answer Q1 above in order to answer points 3 and 4:
			\item Their gains from commitment derive from improvement in bargaining power vis-a-vis the lobby (Schelling conjecture invoked). How does this relate to the gain from commitment in my model?
			\item Top of page 6: ``large enough bargaining power.'' Can I make connection to $\ga(e)$?
			\item Note: in their equation 3, $C$ enters expression for NBS's ($\tau$) in equilibrium, it doesn't disappear as in GH
		\end{enumerate}
\end{itemize}

@@

\end{document}

>>>>

\section{Misc.}
\begin{itemize}
	\item Define $\ga$ before using it
	\item If add back in assumption 1, add Ethier footnote
	\item standardize $\ga(e,s)$, $\ga(e)$, $\ga(s)$ throughout the text
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover [add to conclusion, it's in slides]
\end{itemize}

\section{Deal with ``dynamic preferences'' issue}
	\begin{itemize}
		\item James: need to be more precise about when $\ga$ is evaluated
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}
		\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item DILLENBERGER, D., J. S. LLERAS, P. SADOWSKI, AND N. TAKEOKA (2013): ``A Theory of Subjective Learning,'' Working Paper. 
					\item GUL, F., AND W. PESENDORFER (2004): ``Self-Control and the Theory of Consumption,'' Econometrica, 72 (1), 119-158
					\item JONES, R. A., AND J. M. OSTROY (1984): ``Flexibility and Uncertainty,'' Review of Economic Studies, 51 (1), 13-32
					\item KOOPMANS, T. C. (1964): ``On the Flexibility of Future Preferences,'' in Human Judgments and Optimality, ed. by M. W. Shelly and G. L. Bryan. New York: Wiley.
					\item KREPS, D. M., AND E. L. PORTEUS (1978): ``Temporal Resolution of Uncertainty and Dynamic Choice Theory,'' Econometrica, 46 (1), 185-200.
				\end{itemize}
		\end{itemize}
\section{Take out repeats}
	Especially of references to BS2005: In some parts the paper also seem repeating itself: you review Bagwell and Staiger (2005) in Section 2.2 but you provide another summary of the same paper in Section 3. Again, a revised structure may reduce the overlap, make the paper shorter, and be more to the point.

@@

\section{Lit review}
\begin{itemize}
	\item Find MRC cites (maybe some in Ethier) for why PE shocks can't be addressed
		\begin{itemize}
			\item Bagwell and Staiger 1999 AER
		\end{itemize}
	\item Have to make connection to endogenous papers clearer
		\begin{itemize}
			\item and make clear that GH is isomorphic / provides microfoundations for Baldwin objective function
			\item More on Coates $\&$ Ludema (2001)
		\end{itemize}
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\end{itemize}
	\item Review Bown, Bagwell $\&$ Staiger
	\item Do I include papers like BS2001 (non-repeated) in lit review?
	\item Read Rosendorff $\&$ Milner (2001) [from Cristiane Carneiro at PEIO]
	\item Limao and Tovar 2011
		\begin{enumerate}
			\item Their 2nd (and final) stage is Nash bargaining. Is there an isomorphism to my setup?
			\item It IS clear to take their first, limited case of commitment to tariff cap only (ignore NTB) as analogy for gov't in my model choosing commitment to different tariff level. Need to answer Q1 above in order to answer points 3 and 4:
			\item Their gains from commitment derive from improvement in bargaining power vis-a-vis the lobby (Schelling conjecture invoked). How does this relate to the gain from commitment in my model?
			\item Top of page 6: ``large enough bargaining power.'' Can I make connection to $\ga(e)$?
			\item Note: in their equation 3, $C$ enters expression for NBS's ($\tau$) in equilibrium, it doesn't disappear as in GH
		\end{enumerate}
\end{itemize}

@@

\section{Numeraire}
Do I need to add a numeraire so I can put $e$ in terms of it?

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Rick Bond: need lobbying to use up resources: if it changes net profits, it should also change $\pi$ in $W(\tau,\tau^*)$
	\end{itemize}
\end{document}
